Summary Tables

### 2019-06-21 summary_tables_outcomes.Rmd

sum_and_round_and_print <- function(data,text=''){
  data <- lapply(data, function(x)round(x,round_to))
  data <- lapply(data,function(x)rbind(x,Total=colSums(x)))
  for(city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}

@@

```{r scen_prop = "asis"}
death_rates <- lapply(cities,function(x) death_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(death_rates) <- cities

sum_and_round_and_print(death_rates,"Change in deaths per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
yll_rates <- lapply(cities,function(x) yll_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(yll_rates) <- cities
sum_and_round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

@@

yll_rates <- lapply(cities,function(x) 
  yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')],1,function(z)paste0(z[2],'_',z[1])),rownames(yll_totals[[x]])),]/
    t(repmat(io[[x]]$demographic$population,5,1))*100000)
names(yll_rates) <- cities
sum_and_round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(injury_rates) <- cities
sum_and_round_and_print(injury_rates,"Change in deaths due to injury per 100,000 in ")

pa_rates <- lapply(cities,function(x) pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(pa_rates) <- cities
sum_and_round_and_print(pa_rates,"Change in deaths due to PA per 100,000 in ")

ap_rates <- lapply(cities,function(x) ap_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(ap_rates) <- cities
sum_and_round_and_print(ap_rates,"Change in deaths due to AP per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(injury_rates) <- cities
sum_and_round_and_print(injury_rates,"Change in YLLs due to injury per 100,000 in ")

pa_rates <- lapply(cities,function(x) pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(pa_rates) <- cities
sum_and_round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ")

ap_rates <- lapply(cities,function(x) ap_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(ap_rates) <- cities
sum_and_round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) disease_totals[[x]]/sum(pop_by_age[[x]])*100000)
names(disease_rates) <- cities
sum_and_round_and_print(disease_rates,"Change in deaths due to disease per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) disease_totals[[x]]/sum(pop_by_age[[x]])*100000)
names(disease_rates) <- cities
sum_and_round_and_print(disease_rates,"Change in YLL due to disease per 100,000 in ")
```

>>>>

sum_and_round_and_print <- function(data,text=''){
  data <- lapply(data, function(x)round(x,round_to))
  data <- lapply(data,function(x)rbind(x,Total=colSums(x)))
  for(city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
round_and_print <- function(data,text=''){
  data <- lapply(data, function(x)round(x,round_to))
  for(city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}

@@

```{r scen_prop = "asis"}
death_rates <- lapply(cities,function(x) rbind(death_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(death_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(death_rates) <- cities

round_and_print(death_rates,"Change in deaths per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
yll_rates <- lapply(cities,function(x) rbind(yll_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

@@

yll_rates <- lapply(cities,function(x) 
  rbind(yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')],1,function(z)paste0(z[2],'_',z[1])),rownames(yll_totals[[x]])),]/
    t(repmat(io[[x]]$demographic$population,5,1))*100000, Total=colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) rbind(injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(injury_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(injury_rates) <- cities
round_and_print(injury_rates,"Change in deaths due to injury per 100,000 in ")

pa_rates <- lapply(cities,function(x) rbind(pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in deaths due to PA per 100,000 in ")

ap_rates <- lapply(cities,function(x) rbind(ap_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(ap_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(ap_rates) <- cities
round_and_print(ap_rates,"Change in deaths due to AP per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) rbind(injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(injury_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(injury_rates) <- cities
round_and_print(injury_rates,"Change in YLLs due to injury per 100,000 in ")

pa_rates <- lapply(cities,function(x) rbind(pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ")

ap_rates <- lapply(cities,function(x) rbind(ap_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(ap_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(ap_rates) <- cities
round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) rbind(disease_totals[[x]]/sum(pop_by_age[[x]])*100000, Total=colSums(disease_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(disease_rates) <- cities
round_and_print(disease_rates,"Change in deaths due to disease per 100,000 in ")
```

@@

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) rbind(disease_totals[[x]]/sum(pop_by_age[[x]])*100000, Total=colSums(disease_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(disease_rates) <- cities
round_and_print(disease_rates,"Change in YLL due to disease per 100,000 in ")
```
